|

### 2020-11-29 manuscript/article.Rmd
commit 2 11/28

```{r, message=FALSE, warning=FALSE, echo=FALSE}
# If you need to install any package while knitting the document
r <- getOption("repos")
r["CRAN"] <- "https://cran.rstudio.com/"
options(repos = r)
if (!require("kableExtra")) {
    install.packages("kableExtra")
}
```

@@

Our survey of the scholarship confirms this continuum of positive,
insignificant, and negative results. Out of the 36 coefficients included in our
selected articles, 42\% of them are positive and statistically significant, 22\%
are positive and statistically insignificant, 17\% are negative and
statistically insignificant, and 19\% are negative and statistically
significant. Given this diversity of empirical findings, a systematic review of
the existing evidence may help us reach a meaningful conclusion about the effect
of legislature size on public spending. Meta-analysis is the most appropriate
method for this task. Meta-analysis combines the outcomes of multiple studies
into a single estimation and allows scholars to draw robust conclusions from the
aggregated data \citep{cooper2019handbook,hedges1985statistical}. It can also
identify potential sources of study heterogeneity, enabling researchers to
assess threats to external validity and direct future efforts into more
promising areas of academic inquiry \citep{doucouliagos2008democracy}.

In this letter, we conduct the first meta-analysis that tests the generality of
the "law of $1/n$". We have selected 29 articles that use quantitative methods
to analyse the impact of legislature size over government spending. We run two
sets of models: the first group uses only the main estimates of each paper (42),
while the second set includes all coefficients reported in our sample
(142).\footnote{Although there are 29 papers in our review, we include 42
coefficients in the restricted sample. This is because 13 articles report
separate estimates for the impact of lower and upper house size on government
expenditures. In the full model, we add every outcome reported in the
papers, regardless of whether the coefficient comes from the main tables or
from robustness checks conducted by the original authors. We discuss our
sampling process in the Methods section of this paper and in the Supplementary
Material.} Our independent variables consist of three measures, namely the size
of the lower chamber ($n$), its natural logarithm (log($n$)), and the number of
members in the upper chamber ($k$). We evaluate their effect upon public
expenditure per capita, the natural logarithm of public expenditure per capita,
and government expenditure as a percentage of GDP. We then estimate if the
results vary according to four potential sources of effect heterogeneity.

>>>>

```{r, message=FALSE, warning=FALSE, echo=FALSE}
## Starting

# Knitr options
knitr::opts_chunk$set(fig.pos = "H") # holds figure position
knitr::opts_chunk$set(echo = TRUE)

set.seed(732578) # From random.org

# Needed packages
pkgs <- c("tidyverse", "meta", "metafor",
          "readxl", "compareGroups",
          "knitr", "gridGraphics", "gridExtra",
          "ggpubr", "kableExtra", "magick")

# Install if not already installed
installIfNot <- function(x) {
  if (x %in% rownames(installed.packages()) == FALSE)
    install.packages(x, dependencies = T,
					 repos = "http://cran.us.r-project.org")
}
lapply(pkgs, installIfNot)

# Load packs
lapply(pkgs, require, character.only = T)
rm(pkgs, installIfNot)

# Load datasets
load("../dataset/dataCoefs.RData")

# Build plot function for forest plots
build_forest <- function(mod, capt, lsize = 22, ttl = NULL) {
  # Build dataset for plot
  mod2 <- tibble(
    TE = mod$TE,
    seTE = mod$seTE,
    studlab = mod$studlab,
    lower = mod$lower,
    upper = mod$upper,
    group = "A") %>%
    bind_rows(.,
              aux = tibble(
                TE = c(mod$TE.random, NA),
                seTE = c(mod$seTE.random, NA),
                studlab = c("Overall Effect",
                            "Prediction Interval"),
                lower = c(mod$lower.random,
                          mod$lower.predict),
                upper = c(mod$upper.random,
                          mod$upper.predict),
                group = "B")) %>%
    group_by(studlab) %>%
    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
    ungroup()

  # Graph limits
  limg <- max(abs(c(mod2$lower, mod2$upper)))

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab2, TE),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group),
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
    scale_y_discrete(
      labels = function(x)
        str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(group~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}

dat$scoefnd <- as.character(dat$scoef)
dat$scoefnd[dat$scoefsig=='Positive'&dat$scoef=='Positive'&!is.na(dat$scoefsig)] = 'Positive Significant'
dat$scoefnd[dat$scoefnd=='Positive'] = 'Positive Insignificant'
dat$scoefnd[dat$scoefsig=='Negative'&dat$scoef=='Negative'&!is.na(dat$scoefsig)] = 'Negative Significant'
dat$scoefnd[dat$scoefnd=='Negative'] = 'Negative Insignificant'
```

@@

Our survey of the scholarship confirms this continuum of positive,
insignificant, and negative results. Out of the `r dim(dat)[1]` coefficients included in our
selected articles, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[4])`\% of them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[3])`\%
are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[1])`\% are negative and
statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[2])`\% are negative and statistically
significant. Given this diversity of empirical findings, a systematic review of
the existing evidence may help us reach a meaningful conclusion about the effect
of legislature size on public spending. Meta-analysis is the most appropriate
method for this task. Meta-analysis combines the outcomes of multiple studies
into a single estimation and allows scholars to draw robust conclusions from the
aggregated data \citep{cooper2019handbook,hedges1985statistical}. It can also
identify potential sources of study heterogeneity, enabling researchers to
assess threats to external validity and direct future efforts into more
promising areas of academic inquiry \citep{doucouliagos2008democracy}.

In this letter, we conduct the first meta-analysis that tests the generality of
the "law of $1/n$". We have selected `r length(unique(dat$id))` articles that use quantitative methods
to analyse the impact of legislature size over government spending. We run two
sets of models: the first group uses only the main estimates of each paper (`r dim(dat)[1]`),
while the second set includes all coefficients reported in our sample
(`r dim(fulldat)[1]`).\footnote{Although there are `r length(unique(dat$id))` papers in our review, we include `r dim(dat)[1]`
coefficients in the restricted sample. This is because `r as.numeric(sum(table(table(dat$id))[-1]))` articles report
separate estimates for the impact of lower and upper house size on government
expenditures. In the full model, we add every outcome reported in the
papers, regardless of whether the coefficient comes from the main tables or
from robustness checks conducted by the original authors. We discuss our
sampling process in the Methods section of this paper and in the Supplementary
Material.} Our independent variables consist of three measures, namely the size
of the lower chamber ($n$), its natural logarithm (log($n$)), and the number of
members in the upper chamber ($k$). We evaluate their effect upon public
expenditure per capita, the natural logarithm of public expenditure per capita,
and government expenditure as a percentage of GDP. We then estimate if the
results vary according to four potential sources of effect heterogeneity.
